\input{resumeformatting.tex}
\usepackage{wasysym}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\makeheading{Petr Keil -- Curriculum Vitae}

\thispagestyle{empty}

\section{Contact information}

	German Centre for Integrative Biodiversity Research -- iDiv \\
	Deutscher Platz 5e,  04103 Leipzig, Germany\\
    E-mail: \email{pkeil@seznam.cz}\\
    Personal web and blog: \href{http://www.petrkeil.com}	{www.petrkeil.com}\\

\HRule

\section{Education}

\begin{innerlist}

\item[]{\bf  Ph.D., Ecology} 
\hfill {2006--2010} \\
Department of Ecology, Faculty of Science, {\bf Charles University in Prague}, Czech Republic. Dissertation: \textit{Macroecology of European invertebrates: spatial and temporal patterns extracted from heterogeneous data}. Advisor: \href{http://www.cts.cuni.cz/~storch/}{David Storch}.\\

\item[]{\bf  M.S., Zoology \& Entomology} 
\hfill {2003--2005} \\
Department of Zoology, Faculty of Biology, {\bf University of South Bohemia}, Ceske Budejovice, Czech Republic. Advisor: \href{http://www.entu.cas.cz/en/staff/Martin-Konvicka-r81r/?all_publications=show}{Martin Konvicka}. I spent one semester of 2004 at {\bf Universit\'{e} de Rennes 1}, France, as an EU-funded Erasmus exchange student.\\ 

\item[]{\bf  B.S., {Biology}} 
\hfill {2000--2003} \\
Faculty of Biology, University of South Bohemia, Ceske Budejovice, Czech Republic\\

\end{innerlist}

\HRule

\section{Professional experience}

\begin{innerlist}

\item[]{\bf Postdoc} 
\hfill {2015--present} \\
German Centre for Integrative Biodiversity Research -- \textbf{iDiv}, Leipzig, Germany.\\

\item[]{\bf Postdoc} 
\hfill {2011--2014} \\
Dept. of Ecology and Evolutionary Biology, {\bf Yale University}, USA. First year funded by \href{http://www.mappinglife.org/}{Map of Life} project of \href{http://jetzlab.yale.edu/people/walter-jetz}{Walter Jetz}. Since 2012 funded by EU Marie-Curie fellowship.\\

\item[]{\bf Research associate} 
\hfill {2011, 2012--2015} \\ 
Center for Theoretical Study -- CTS, {\bf Charles University in Prague}, Czech Republic. \\

\item[]{\bf Early--stage research trainee} 
\hfill {2008 (5 months), 2009 (2 months)} \\ 
Faculty of Biological Sciences, {\bf University of Leeds}, UK. 
Funded by a Marie Curie Fellowship for early--stage researchers. Advisors: \href{http://www.fbs.leeds.ac.uk/staff/profile.php?tag=Biesmeijer}{Koos Biesmeijer} \& \href{http://www.fbs.leeds.ac.uk/staff/profile.php?tag=Kunin}{William E. Kunin}.\\

\item[]{\bf Research associate} 
\hfill {2007--2010} \\ 
Dept. of Ecology, Faculty of Science, Charles University in Prague, Czech Republic. The position was funded from various grants, and was held parallel to my Ph.D. studies.\\

\item[]{\bf Technician}
\hfill {2006}\\
Department of Zoology, {\bf University of Cambridge}, UK. Six months as a technician in the lab of \href{http://www.zoo.cam.ac.uk/zoostaff/hedwig/index.html}{Berthold Hedwig}. Performed behavioural experiments with crickets.\\\\\\\\

\end{innerlist}

\newpage

\HRule

\section{Submitted manuscripts}

\begin{etaremune}
\item Viana D.S., \underline{Keil P.} \& Jeliazkov A. (2019) Partitioning environment and space in species-by-site matrices: a comparison of methods for community ecology and macroecology. 

\item \underline{Keil P.} (2019) Z-scores unite pairwise indices of ecological similarity and association for binary data.

\item Sporbert M., \underline{Keil P.}, ... \& Welk E. (2019) No general transferability between small-scale abundance and large-scale distribution of European plants. 

\item Craven D., van der Sande M.T., ..., \& \underline{Keil P.} (2019) A cross-scale assessment of productivity-diversity relationship. 

\end{etaremune}

\section{Peer-reviewed articles}

\begin{etaremune}

\item Isaac N.J.B., Jarzyna M., \underline{Keil P.}, ... \& O'Hara B. (2019) Data integration for large scale models of species distributions. \textit{\textbf{Trends in Ecology and Evolution}}, in press.

\item \underline{Keil P.} \& Chase J.M. (2019) Global patterns and drivers of tree diversity integrated across a continuum of spatial grains. \textit{\textbf{Nature Ecology and Evolution}}, 3: 390-399. [\href{https://www.nature.com/articles/s41559-019-0799-0}{link}].

\item Sporbert M. et al. (2019) Assessing sampling coverage of species distribution in biodiversity databases. \textit{\textbf{Journal of Vegetation Science}}, 30: 620-632. \href{https://onlinelibrary.wiley.com/doi/full/10.1111/jvs.12763}{link}].

\item Ren H., \underline{Keil P.} et al. \& Jetz W. (2019) Environment- and trait-mediated scaling of tree occupancy in forests worldwide. \textit{\textbf{Global Ecology and Biogeography}}, 28: 1155-1167. [\href{https://onlinelibrary.wiley.com/doi/full/10.1111/geb.12922}{link}].

\item Jetz W. et al. (2019) Essential biodiversity variables for mapping and monitoring species populations. \textit{\textbf{Nature Ecology and Evolution}}, 3: 539-551. [\href{https://www.nature.com/articles/s41559-019-0826-1}{link}].

\item \underline{Keil P.}, MacDonald A.A.M., Ramirez K.S., Bennett J.M., Garcia-Pena G.E., Yguel B., Bourgeois B. \& Meyer C. (2018)  Macroecological and macroevolutionary patterns emerge in the universe of GNU/Linux operating systems. \textit{\textbf{Ecography}}, 41: 1788-1800. [\href{https://onlinelibrary.wiley.com/doi/full/10.1111/ecog.03424}{link}]

\item \underline{Keil P.}, Pereira H.M., Cabral J.S., Chase J.M., May F., Martins I.S. \& Winter M. (2018) Spatial scaling of extinction rates: theory and data reveal non-linearity, and a major upscaling and downscaling challenge. \textit{\textbf{Global Ecology and Biogeography}}, 27: 2-13. [\href{http://onlinelibrary.wiley.com/doi/10.1111/geb.12669/abstract}{link}]

\item Shade A., Dunn R.R., Blowes S.A., \underline{Keil P.}, Bohannan B.J.M., Hermann M., Kusel K., Lennon J.T., Sanders N.J., Storch D. \& Chase J. (2018) Macroecology to unite all life, great and small. \textit{\textbf{Trends in Ecology and Evolution}}, 33: 731-744. [\href{https://www.sciencedirect.com/science/article/pii/S0169534718301861?via%3Dihub}{link}]

\item Dormann C.F. \textit{et al.} (2018) Model averaging in ecology: a review of Bayesian, information-theoretic and tactical approaches. \textit{\textbf{Ecological Monographs}}, 88: 485-504. [\href{https://esajournals.onlinelibrary.wiley.com/doi/10.1002/ecm.1309}{link}]

\item Gratton P., Marta S., Bocksberger G., Winter M., \underline{Keil P.}, Trucchi E. \& Kuhl H. (2017) Which latitudinal gradients for genetic diversity? \textit{\textbf{Trends in Ecology and Evolution}}, 32: 724-726. [\href{https://www.sciencedirect.com/science/article/pii/S0169534717301830?via%3Dihub}{link}]

\item \underline{Keil P.}, Storch D. \& Jetz W. (2015) On the decline of biodiversity due to area loss. \textit{\textbf{Nature Communications}}, 6: 8837. [\href{https://www.nature.com/articles/ncomms9837}{link}]

\item Quintero I., \underline{Keil P.}, Jetz W. \& Crawford F.W. (2015) Historical biogeography using species geographical ranges. \textit{\textbf{Systematic Biology}}, 64: 1059-1073. [\href{http://sysbio.oxfordjournals.org/content/64/6/1059.short}{link}] 

\item Tropek R., Sedlacek O., Beck J., \underline{Keil P.}, Musilova Z., Simova I. \& Storch D. (2014) Comment on ``High resolution global maps of 21-st century forest cover change". \textit{\textbf{Science}}, 344: 981. [\href{http://www.sciencemag.org/content/344/6187/981.4.full}{link}] 

\item \underline{Keil P.}, Wilson A.O. \& Jetz W. (2014) Uncertainty, priors, autocorrelation and disparate data in downscaling of species distributions. \textit{\textbf{Diversity and Distributions}}, 20: 797-812. [\href{http://onlinelibrary.wiley.com/doi/10.1111/ddi.12199/abstract}{link}]

\item Sturrock H.J.W, Cohen J.M., \underline{Keil P.}, Tatem A.J., Menach A.L., Ntshalinthsali N.E., Hsiang M.S. \& Gosling R.D. (2014) Fine-scale malaria risk mapping from routine aggregated data. \textit{\textbf{Malaria Journal}}, 13: 421.

\item \underline{Keil P.} \& Jetz W. (2014) Downscaling the environmental associations and spatial patterns of species richness. \textit{\textbf{Ecological Applications}}, 20: 797-812. [\href{http://www.esajournals.org/doi/abs/10.1890/13-0805.1?af=R&}{link}] 

\item Pechacek P., Stella D., \underline{Keil P.} \& Kleisner K. (2014) Environmental effects on the shape variation of male ultraviolet patterns in the brimstone butterfly (\textit{Gonepteryx rhamni}, Pieridae, Lepidoptera). \textit{\textbf{Naturwissenschaften}}, 101, 1055-1063.  [\href{http://link.springer.com/article/10.1007/s00114-014-1244-5}{link}] 

\item Straka J., Cerna K., Machackova L., Zemenova M. \& \underline{Keil P.} (2014) Life span in the wild: the role of activity and climate in natural populations of bees. \textit{\textbf{Functional Ecology}}, 28: 1235-1244.
[\href{http://onlinelibrary.wiley.com/doi/10.1111/1365-2435.12261/abstract}{link}]

\item \underline{Keil P.}, Belmaker J., Wilson A.M., Unitt P. \& Jetz W. (2013) Downscaling of species distribution models: a hierarchical approach. \textit{\textbf{Methods in Ecology and Evolution}}, 4: 82-94. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.2041-210x.2012.00264.x/abstract}{link}]

\item Carvalheiro L., Kunin W.E., \underline{Keil P.} \& 16 authors (2013) Biodiversity declines and biotic homogenization have slowed down for NW--European pollinators and plants. \textit{\textbf{Ecology Letters}}, 16: 870-878. [\href{http://onlinelibrary.wiley.com/doi/10.1111/ele.12121/abstract}{link}]

\item Storch D., \underline{Keil P.} \& Jetz W. (2012) Universal species--area and endemics--area relationships at continental scales. \textit{\textbf{Nature}}, 488: 78-81. [\href{http://www.nature.com/nature/journal/v488/n7409/full/nature11226.html}{link}]

\item \underline{Keil P.}, Schweiger O., Kuhn I., Kuussaari M., Kunin W.E., Settele J., Henle K., Brotons L., Pe’er G., Lengyel S., Moustakas A., Steinicke H. \& Storch D. (2012) Patterns of beta diversity in Europe: the role of climate, land cover and distance across scales. \textit{\textbf{Journal of Biogeography}}, 39: 1473-1486. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1365-2699.2012.02701.x/abstract}{link}]

\item Kleisner K., \underline{Keil P.} \& Jaros F. (2012) Biogeography of elytral ornaments in Palearctic genus Carabus: disentangling the effects of space, evolution and environment at a continental scale. \textit{\textbf{Evolutionary Ecology}}, 26: 1025-1040. [\href{http://link.springer.com/article/10.1007%2Fs10682-011-9537-z}{link}]

\item Henle et al. (2012) Nature Conservation -- a new dimension in Open Access publishing bridging science and application. \textit{\textbf{Nature Conservation}}, 1: 1-10. [\href{http://www.pensoft.net/journals/natureconservation/article/3081/abstract/}{link}]

\item \underline{Keil P.}, Biesmeijer J.C., Barendregt A., Reemer M. \& Kunin W.E. (2011) Biodiversity change is scale--dependent: an example from dutch and UK hoverflies (Diptera, Syrphidae). \textit{\textbf{Ecography}}, 34: 392-401. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1600-0587.2010.06554.x/abstract}{link}]

\item Simova I., Storch D., \underline{Keil P.}, Boyle B., Phillips O.L. \& Enquist B.J. (2011) Global species--energy relationship in forest plots: role of abundance, temperature and species' climatic tolerances. \textit{\textbf{Global Ecology and Biogeography}}, 6: 842-856. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1466-8238.2011.00650.x/abstract}{link}] 

\item \underline{Keil P.}, Herben T., Rosindell J. \& Storch D. (2010) Predictions of Taylor's power law, density dependence and pink noise from a neutrally modelled time series. \textit{\textbf{Journal of Theoretical Biology}}, 265: 78-86. [\href{http://www.sciencedirect.com/science/article/pii/S0022519310001979}{link}]

\item Sizling A.L., Storch D. \& \underline{Keil P.} (2009) Rapoport's rule, species tolerances, and the latitudinal diversity gradient: geometric considerations. \textit{\textbf{Ecology}}, 90: 3575-3586. [\href{http://www.esajournals.org/doi/abs/10.1890/08-1129.1?journalCode=ecol}{link}]

\item \underline{Keil P.} \& Hawkins B.A. (2009) Grids versus regional species lists: are broad--scale patterns of species richness robust to the violation of constant grain size? \textit{\textbf{Biodiversity and Conservation}}, 18: 3127-3137. [\href{http://link.springer.com/article/10.1007%2Fs10531-009-9631-5}{link}]

\item Dixon A.F.G., Honek A., \underline{Keil P.}, Kotela M.A., Sizling A.L. \& Jarosik V. (2009) Relationship between the minimum and maximum temperature thresholds for development in insects. \textit{\textbf{Functional Ecology}}, 23: 257-264. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1365-2435.2008.01489.x/abstract}{link}]

\item \underline{Keil P.}, Dziock F. \& Storch D. (2008) Geographical patterns of hoverfly (Diptera, Syrphidae) functional groups in Europe: inconsistency in environmental correlates and latitudinal trends. \textit{\textbf{Ecological Entomology}}, 33: 748-757. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1365-2311.2008.01032.x/abstract}{link}]

\item Langrova I., Makovcova K., Vadlejch J., Jankovska I., Petrtyl M., Fetchner J., \underline{Keil P.}, Lytvynets A. \& Borkovcova M. (2008) Arrested development of sheep strongyles: onset and resumption under field conditions of Central Europe. \textit{\textbf{Parasitology Research}}, 103: 387-392. [\href{http://link.springer.com/article/10.1007%2Fs00436-008-0984-6}{link}]

\item \underline{Keil P.}, Simova I. \& Hawkins, B.A. (2008) Water-energy and the geographical species richness pattern of European and North African dragonflies (Odonata). \textit{\textbf{Insect Conservation and Diversity}}, 1: 142-150. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1752-4598.2008.00019.x/abstract}{link}]

\item Konvicka M., Novak J., Benes J., Fric Z., Bradley J., \underline{Keil P.}, Hrcek J., Chobot K. \& Marhoul P. (2007) The last population of the Woodland Brown butterfly (Lopinga achine) in the Czech Republic: habitat use, demography and site management. \textit{\textbf{Journal of Insect Conservation}}, 12: 549-560. [\href{http://link.springer.com/article/10.1007%2Fs10841-007-9087-4}{link}]

\item \underline{Keil P.} \& Konvicka M. (2005) Local species richness of Central European hoverflies (Diptera: Syrphidae): a lesson taught by local faunal lists. \textit{\textbf{Diversity and Distributions}}, 11: 417-426. [\href{http://onlinelibrary.wiley.com/doi/10.1111/j.1366-9516.2005.00172.x/abstract}{link}]

\item \underline{Keil P.} (2005) Microhabitat preferences of Stiletto-flies larvae (Diptera: Therevidae) in mountain primeval forest. \textit{\textbf{Studia Dipterologica}}, 12(1): 87-92. [\href{http://www.studia-dipt.de/con121.htm}{link}]
\end{etaremune}

\HRule

\section{Chapters, preprints, proceedings}
\begin{etaremune} 

\item Bitner J., Schejbalova A., Bartova K., Varella J., Krejcova L., Weiss P., Kleisner K., Keil P. \& Kvapilova K. (2015) Prevalence of zoophilia in Czech sado-masochistic community. \textit{\textbf{Journal of Sexual Medicine}}, 12: 41-41.

\item Keil P. (2014) Limits of uncertainty about estimates of probability of ecological events. \textit{\textbf{PeerJ PrePrints }}, 2:e446v1. [\href{https://peerj.com/preprints/446/}{link}]

\item Storch D., Keil P. \& Kunin W.E. (2014) Scaling communities and biodiversity. Pages 66-77. In: \textit{\textbf{Scaling in Ecology and Biodiversity Conservation}}, Pensoft. Eds: Henle et al. [\href{http://ab.pensoft.net/articles.php?id=1169}{link}]
 
\end{etaremune}

\HRule

\section{Service for Journals}

Associate editor of \textit{\textbf{Global Ecology and Biogeography}} (Wiley)

\medskip

Associate editor of \textit{\textbf{Nature Conservation}} (Pensoft Publishers) \\
\medskip

{\bf Reviewer for}: \textit{Ecology Letters, Nature Ecology \& Evolution, Nature Communications, Ecography, Journal of Biogeography, Global Ecology and Biogeography, Journal of Animal Ecology, Diversity and Distributions, Oikos, Perspectives in Plant Ecology Evolution and Systematics, Journal of Geographic Information Systems, Acta Oecologica, Methods in Ecology and Evolution, Biodiversity and Conservation, Biological Conservation, Population Ecology, Ecological Modelling, European Journal of Entomology, Polish Journal of Ecology, Journal of Vegetation Science, Ecology \& Evolution, Ethology Ecology and Evolution, Ecological Applications, American Naturalist, Zapadoceske Entomologicke Listy.}

\HRule

%\newpage
\section{Citation \\ Metrics}

Accessed 20 Sep 2019:

\begin{itemize}
\item \textbf{Google Scholar:} 1342 citations, h-index  = 19.
\item \textbf{ISI Web of Science:} 844 citations (819 without self-citations), h-index = 15.
\end{itemize}


\HRule

\section{Students}

\begin{innerlist}

\item[]{\bf Maria Sporbert}, PhD student at Martin Luther University of Halle-Wittenberg (co-advisor, ongoing)

\item[]{\bf Eduardo Arle}, PhD student at Leipzig University (PhD advisory commitee member, ongoing)

\item[]{\bf Amanda Ratier Backes}, PhD student at Leipzig University (PhD advisory commitee member, ongoing)

\medskip

\item[]{\bf Adam Klimes}, Master student at Charles University (advisor, finished in 2016)

\end{innerlist}

\HRule

\section{Lecturing}

\begin{innerlist}


\item[]{\bf Bayesian Biostatistics} - University of Leipzig, Charles University
\hfill {2014-2017}\\
Three-day intensive practical course for 15-20 students.
[\href{http://www.petrkeil.com/?p=1881}{link}]

\medskip

\item[]{\bf Spatial Biodiversity Analysis Methods} - Yale University, USA
\hfill {2013}\\
Taught together with Adam M. Wilson, Giuseppe Amatulli and Walter Jetz.
[\href{https://sites.google.com/site/spatialbiodiversity/home}{link}]

\medskip

\item[]{\bf Spatial Scale in Biodiversity Science} - Yale University, USA
\hfill {2012} \\
Graduate course (Yale EEB 713 01 - S13) for ca. 10 students, taught with prof. Walter Jetz. [\href{http://pantheon.yale.edu/~pk327/pdf/Keil&Jetz_syllabus.pdf}{link to syllabus}]

\medskip

\item[]{\bf Course of R Programming} - Charles University, Czech Republic
\hfill {2009--2011} \\
Graduate course of R programming \textit{``R for Life"} for ca. 20 students at Faculty of Science.

\medskip

\item[]{\bf Foundations of Ecology} - Charles University, Czech Republic
\hfill {2007--2009} \\
Principal lecturer of graduate course \textit{``Foundations of Ecology"} for ca. 20 students of Social and Cultural Ecology at Faculty of Humanities (FHS).

\end{innerlist}

\HRule


\section{3rd party funding}

\begin{innerlist}

\item[]{\bf sDiv Fellowship, iDiv, Leipzig, Germany}
\hfill {2015--2017} \\
2-year independent postdoctoral project ``\textit{Assessing extinction: Crossover of geometrical, macroecological and Bayesian perspectives}".
\\

\item[]{\bf Marie Curie Fellowship (IOF)}
\hfill {2012--2015} \\
EU FP7-PEOPLE, Project WORLDIVERSITY -- ``\textit{Linking global species and beta diversity to individual species distributions at multiple phylogenetic and spatial scales}"  (\# 302868). Host: Yale University, USA.
\\

\item[]{\bf Grand Agency of Charles University}
\hfill {2008--2010} \\
Co-PI (with Irena Simova) on project GAUK106108  \textit{``The effect of energy availability and environmental heterogeneity on species diversity of plants and invertebrates"}. 

\end{innerlist}

\HRule

\section{Awards}

Dean's prize for the \textbf{best PhD thesis} defended in 2010 at Faculty of Science, Charles University in Prague.

\HRule

\section{Skills}

{\bf Software}: R, C++, Windows, Linux, Bash, Grass GIS, ArcGIS, QGIS, OpenBUGS, JAGS, STAN, Canoco, \LaTeX, HTML, CSS, SQL, Markdown, WordPress, Graphic editors (GIMP, InkScape, Corel and Adobe suites).

\medskip

{\bf Statistics}: GLM, hierarchical (mixed-effects) models, GAM, ordinations, spatial statistics, time series analysis, survival analysis, structural equations models, data visualization, machine learning, model selection, model diagnostics, predictive inference, Monte-Carlo tests, bootstrap, Bayesian inference, likelihood optimization.

\medskip

{\bf Languages}: English (excellent); German, Spanish, French (intermediate); Czech (nat.).

\HRule

\section{References}


Prof. \textbf{Jonathan M. Chase}, iDiv. \phone +49 341 9733120. \href{mailto: jonathan.chase@idiv.de}{jonathan.chase@idiv.de}

\medskip

Dr. \textbf{Marten Winter}, iDiv. \phone +49 341 9733129. \href{mailto: marten.winter@idiv.de}{marten.winter@idiv.de}

\medskip

Prof. \textbf{Walter Jetz}, Yale University. \phone +1 2034327540. \href{mailto:walter.jetz@yale.edu}{walter.jetz@yale.edu}

\medskip

Prof. \textbf{David Storch}, Charles University. \phone +420 221183535. 
\href{mailto:storch@cts.cuni.cz}{storch@cts.cuni.cz}

\medskip

Prof. \textbf{William Kunin}, University of Leeds. \phone +440 1133432857. \href{mailto:w.e.kunin@leeds.ac.uk}{w.e.kunin@leeds.ac.uk}






\end{document}\grid
\grid
